{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-04-25 thesis/overview.tex
talk abt psu and pebwine

In the course of a semester, students work on five programming assignments;
the first two are individual, and the remaining three are the products of two-person teams.
I will focus on the third and fourth of these, the thread library and kernel,
called ``P2'' and ``P3'' respectively (the project numbers start at 0).
The other three (a stack-crawling backtrace utility, a bare-metal game with device drivers, and a small extension to the P3 kernel) are not of concern in this thesis.
The course's prerequisite is Introduction to Computer Systems \cite{sigcse01:CSaPP}.
Both P2 and P3 are built using the {\em Pebbles} system call specification, outlined in Table~\ref{tab:syscalls}

@@

>>>>

The Pebbles kernel architecture
is used at CMU in 15-410, Operating System Design and Education \cite{kspec,thrlib}.
In the course of a semester, students work on five programming assignments;
the first two are individual, and the remaining three are the products of two-person teams.
I will focus on the third and fourth of these, the thread library and kernel,
called ``P2'' and ``P3'' respectively (the project numbers start at 0).
The other three (a stack-crawling backtrace utility, a bare-metal game with device drivers, and a small extension to the P3 kernel) are not of concern in this thesis.
The course's prerequisite is Introduction to Computer Systems \cite{sigcse01:CSaPP}.
Both P2 and P3 are built using the {\em Pebbles} system call specification, outlined in Table~\ref{tab:syscalls}

@@

\subsubsection{Use at other universities}

\newcommand\psuos{CMPSC 473\xspace}

In the Spring 2018 semester,
the Operating Systems class at Penn State University (henceforth \psuos and PSU, respectively)
offered the P2 thread library project as part of its curriculum.
Students in this class implemented P2 working alone rather than in pairs,
skip the {\tt swexn} automatic stack growth portion,
and rather than running their code with a reference Pebbles kernel binary in a simulator,
use the Pebwine emulation layer \cite{pebwine}
to run Pebbles-compatible program binaries in the Linux userspace.
Otherwise, the project is identical to CMU 15-410's P2.
